\documentclass[10pt,a4paper,ragged2e,withhyper]{cvclass}
\geometry{left=0cm,right=0cm,top=0cm,bottom=0cm,columnsep=0.0cm}

\usepackage{paracol}

\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  % If using pdflatex:
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  % \usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Change the colours if you want to
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{DDDDDD}
% \definecolor{Blue}{HTML}{003D74}
\definecolor{Blue}{HTML}{473D8F}
\definecolor{DarkBlue}{HTML}{2E284E}
\colorlet{name}{white}
\colorlet{tagline}{white}
\colorlet{heading}{Blue}
\colorlet{headingrule}{black}
\colorlet{subheading}{black}
\colorlet{accent}{black}
\colorlet{emphasis}{Blue}
\colorlet{body}{white}
\colorlet{headingbg}{DarkBlue}

% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\small}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\bfseries}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faSquareFull}
\newcommand{\dt}{ $\cdot$~}

%% sample.bib contains your publications
\addbibresource{main.bib}

\begin{document}

\name{Trey Wilkinson}
\tagline{Full Stack Developer}

\personalinfo{%
  \email{winston.trey.wilkinson@gmail.com}
  \homepage{treywilkinson.com}
  \github{t-wilkinson}
  % \mailaddress{6402, Tisdale Ter}
  \location{Bethesda MD, 20817}
  % \linkedin{your_id}
  % \phone{000-000-0000}
}

\columnratio{0.3}
\begin{paracol}{2}

\newtcolorbox{mycolumn}[1][]{height=845pt, arc=0mm, boxrule=0mm, #1}

\begin{mycolumn}[colback=Blue]
\colorlet{body}{white}
\colorlet{emphasis}{white}
\colorlet{accent}{white}

\renewcommand{\cvsection}[2][]{%
  \medskip%
  \ifstrequal{#1}{}{}{\marginpar{\vspace*{\dimexpr1pt-\baselineskip}\raggedright\input{#1}}}%
  {\color{heading}\cvsectionheading{#2}}
  \color{body}
}

\makecvheader

\cvsection{Skills}

    \begin{cvskillsection}{Frontend}{0.8}
        \item JavaScript\dt TypeScript
        \item React\dt React Native
        \item CSS3\dt SCSS\dt HTML5
        \item Responsive
    \end{cvskillsection}

    \begin{cvskillsection}{Backend}{0.8}
        \item Node.js\dt Next.js\dt Express
        \item REST\dt GraphQL
        \item SQL\dt MongoDB\dt Redis
        \item Nginx\dt Strapi
    \end{cvskillsection}

    \begin{cvskillsection}{Others}{}
        \item AWS
        \item Git\dt Nix
        \item Linux\dt Bash
        \item CI\dt CD
        \item Python\dt Haskell\dt Go\dt Rust
    \end{cvskillsection}

\cvsection{Interests}
    \begin{cvskillsection}{Computers}{}
        \item Machine Learning
        \item Information Security
        \item System Administration
    \end{cvskillsection}

    \begin{cvskillsection}{Math}{}
        \item Category Theory
        \item Homotopy Type Theory
        \item Calculus
        \item Linear Algebra
    \end{cvskillsection}

    \begin{cvskillsection}{Others}{}
        \item Electric Guitar
    \end{cvskillsection}

\cvsection{Education}
    \cvevent{Mary Baldwin University}{}{2018 -- 2019}{}3.6 GPA

    \medskip
    \cvevent{Walter Johnson High School}{}{2013 -- 2018}{}

\end{mycolumn}

\switchcolumn

\begin{mycolumn}
\colorlet{body}{black}
    A focused, driven, and adaptable individual with a passion for learning, creating, and problem-solving. A natural and proactive leader. Three years of experience in web development.

\cvsection{Projects}
    \begin{cvdateevent}{2021--01}{20201-01}{\href{http://ai.treywilkinson.com}{Neural Style Transfer}}{NST Implementation}
        \begin{itemize}
            \item NST uses a trained deep neural network to combine the style of one image and the content of another.
            \item Used React to quickly develop an interesting UI.
            \item Used Next.js to power both the frontend and backend.
            \item Wrote a script in Python using PyTorch to implement a NST algorithm which is applied to user-provided images.
        \end{itemize}
    \end{cvdateevent}
    \divider\\

    \begin{cvdateevent}{2020--06}{2020--12}{\href{https://kleanstudio.com}{Klean Studios}}{Music recording studio}
        \begin{itemize}
            \item Used React, TypeScript, and Tailwind to develop a tailored UI and UX.
            \item Used Node.js and Express to develop a REST compliant architecture.
            \item Created a user dashboard, integrated with Stripe, and an admin dashboard, to automate most business and site functionality.
            \item Used PostgreSQL to provide searching functionality for the dashboard.
            \item Automated hosting on an EC2 instance running Nginx with Jenkins and my Linux knowledge.
        \end{itemize}
    \end{cvdateevent}
    \divider\\

    \begin{cvdateevent}{2020--12}{2021--01}{\href{http://penguins.treywilkinson.com}{Penguin Sweaters}}{Promote penguin conservation efforts}
        \begin{itemize}
            \item Drove the UI and UX with React, TypeScript, and SCSS.
            \item Used a Next.js server to query Strapi endpoints using GraphQL.
            \item Hosted site on an EC2 instance running Nginx.
        \end{itemize}
    \end{cvdateevent}

\cvsection{Experience}
    \begin{cvdateevent}{2015}{2020}{Window Cleaning}{Wells Window Cleaning}
        \begin{itemize}
            \item Professionally cleaned windows with a small team at residences of high portfolio individuals in the Washington DC area.
            \item Developed attention to detail and strong work ethic as I strived to provide only the best results for clients.
            \item Learned risk management and communication in order to work safely and effectively.
            \item Developed problem-solving techniques and creative thinking as I accomplished difficult tasks even when lacking the necessary tools.
        \end{itemize}
    \end{cvdateevent}
    \divider\\

    \begin{cvdateevent}{2014}{2015}{Entrepreneurial Art Internship}{Arts on the Block}
        \begin{itemize}
            \item Created commissioned artwork at a non-profit business for companies in the Washington DC area.
            \item Worked with a group of individuals to design, create, and install commissioned artwork, which required time management, communication, planning, and resourcefulness.
        \end{itemize}
    \end{cvdateevent}
    \divider\\

    \begin{cvdateevent}{2008}{2016}{Eagle Scout}{Award earned in 2016}
        \begin{itemize}
            \item Conceptualized personal community service project, fundraised from local organizations. Lead, organized, and collaborated with ten volunteers over two weeks to provide lasting services for a local, under-funded elementary school.
            \item Consistently lead and managed activities with over 15 individuals, requiring organization, communication, and risk management.
        \end{itemize}
    \end{cvdateevent}

\end{mycolumn}
\end{paracol}

\end{document}
